Ornaments as indicators of social changes and cultural practices in northeastern Taiwan before and after European colonial period

### 2019-12-10 analysis/paper/paper.Rmd
update C14 ages plot

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  cache = TRUE,
  fig.path = "../figures/"
)
# prepare for Antiquity https://antiquity.ac.uk/submit-paper
# should be no more than 13.5cm wide and at a minimum resolution of 300dpi. 
# not exceed 6000 words excluding figures, tables, highlights 
image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm 
```

@@

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The y-axis represents summed probability and the x-axis is the date in calendar years. Produced with the BChronDensity() function in program R's Bchron package (Parnell et al. 2008)."}

@@

# save the dataframe
write.csv(kw_age_cali_df_tidy, here("analysis/data/raw_data/kwl_cal_dates.csv"))

# have a look at the output
par(mfrow = c(2, 3))
plot(kw_dates_with_error_calibrated)

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))
       ))
invisible(dev.off())

#plot it
plot(kw_ages_densities,
     xlab= "Years BC")

@@

```{r C14-table-data}
cal_kw_dates <- readr::read_csv(here("analysis", "data", "raw_data", "kwl_cal_dates.csv"))

table_kw_dates <-
  kw_dates %>% 
  mutate(`Depth related to sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  mutate(Period = as.factor(Period)) %>% 
  mutate(Period = factor(Period,
                       level = c("pre-European", 
                                 "European", 
                                 "post-European"))) %>% 
  arrange(Period) %>% 
  left_join(cal_kw_dates, "Pit-Layer") %>% 
  dplyr::select("Period", "Pit-Layer", "Depth related to sea level (cm)", "Date BP", "Calibrated date (95% conf. level)", "Details")

>>>>

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  cache = TRUE,
  dpi = 300,
  fig.path = "../figures/"
)
# prepare for Antiquity https://antiquity.ac.uk/submit-paper
# should be no more than 13.5cm wide and at a minimum resolution of 300dpi. 
# not exceed 6000 words excluding figures, tables, highlights 
image_width_1_col_inch = 90/25.4 # image Single column	w = 90 mm 
image_width_2_col_inch = 190/25.4 # image Double column w = 190 mm 
```

@@

```{r C14-data, fig.cap= "Summed probability distributions for dates from Kiwulan. The dark line represents the summed probabilities of all radiocarbon ages, and the grey lines in the background are the probabilities of individual ages. Grey rectangles indicate the approximate chronology of the major archaeological components of the deposit. Ages calibrated with the Bchron package (Parnell et al. 2008). "}

@@

# we can combine all the calibrated dates into a single plot, like this
kw_ages_densities <- 
  with(kw_dates_with_error,
       rrtools:::quietly( # suppress the progress bar
         BchronDensity(
         ages = rce,
         ageSds = se,
         calCurves = rep('intcal13',
                         length(kw_dates_with_error$rce))
       ,
       store_density=TRUE))
  )

# plot it
# plot(kw_ages_densities)

kw_ages_densities_df <- 
  tibble(ageGrid = kw_ages_densities$ageGrid,
         densities = kw_ages_densities$densities)

kw_ages_densities_dfs <- 
  map_df(kw_ages_densities$calAges, 
      ~tibble(ageGrid = .x$ageGrid, 
              densities = .x$densities), .id = 'date') %>% 
  mutate(dens_to_one = densities / sum(densities))

lower_component <- c(1300, 800)
upper_component <- c(600, 100)

lines_for_periods <- 
  tibble(bx = c(324,   # start of Euro contact, 1626 AD
               182),  # start of Chinese contact, 1768 AD
          by = c(0, 0),
          byend = c(0.00175),
          bxend = bx)

ggplot() +
    geom_area(data = kw_ages_densities_dfs,
            aes(ageGrid,
                dens_to_one,
                group = date),
            fill = "grey80",
            alpha = 0.4,
            position = 'identity') +
  geom_line(data = kw_ages_densities_df,
            aes(ageGrid,
                densities)) +
  geom_segment(data = lines_for_periods,
              aes(x = bx, 
                  y = by, 
                  xend = bxend, 
                  yend = byend),
               colour = c("red", "blue")) +
  annotate("rect", xmin = 100, xmax = 600, 
                   ymin = 0, ymax = lines_for_periods$byend[1],
           fill = "grey80",
           alpha = 0.3) +
    annotate("text", x = 350, y = 0.0022,
           label = "Upper component",
           size = 2) +
    annotate("rect", xmin = 1300, xmax = 800,
                   ymin = 0, ymax = lines_for_periods$byend[1],
           fill = "grey80",
           alpha = 0.3) +
      annotate("text", x = 1050, y = 0.00220,
           label = "Lower component",
           size = 2)  +
  theme_minimal(base_size = 8) +
  xlab("calibrated years BP") +
  ylab("Density") +
  coord_fixed(ratio = 400000)

@@

```{r C14-table-data}
table_kw_dates <-
  kw_dates %>% 
  mutate(`Depth related to sea level (cm)` = paste0(Depth1, " to ", Depth2)) %>% 
  mutate(`Pit-Layer` = paste0(Square, "-", Layer)) %>% 
  mutate(Period = as.factor(Period)) %>% 
  mutate(Period = factor(Period,
                       level = c("pre-European", 
                                 "European", 
                                 "post-European"))) %>% 
  arrange(Period) %>% 
  left_join(kw_age_cali_df_tidy, "Pit-Layer") %>% 
  dplyr::select("Period", "Pit-Layer", "Depth related to sea level (cm)", "Date BP", "Calibrated date (95% conf. level)", "Details")
